### 2020-10-23 README.Rmd
little example
starting to add small example

run_scbi <- TRUE
run_bw <- TRUE
```

@@

```{r, eval = run_bw}
# Big Woods
set.seed(76)
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, verbose = FALSE,
  # Some guess work in figuring this out:
  k = 28, xOffset = 0.5, yOffset = 0
)

@@

```{r, eval = run_scbi}
# SCBI
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, yOffset = 0.9999, k = 9, verbose = FALSE
)

@@

>>>>

run_scbi <- FALSE
run_bw <- FALSE
small_example <- TRUE
```

@@

```{r, eval = run_bw}
# Big Woods
set.seed(76)
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = cv_fold_size, verbose = FALSE,
  # Some guess work in figuring this out:
  k = 28, xOffset = 0.5, yOffset = 0
)

@@

```{r, eval = run_scbi}
# SCBI
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = cv_fold_size, yOffset = 0.9999, k = 9, verbose = FALSE
)

@@

### Using small example

```{r, eval = small_example}
# Read in census files
data(census_df1_ex, census_df2_ex)

# Filter out resprouts
census_df2_ex_no_r <- census_df2_ex %>%
  filter(!str_detect(codes, 'R'))

id <- 'ID'

ex_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(census_df1_ex, census_df2_ex_no_r, id) %>%
  mutate(
    sp = to_any_case(sp),
    sp = as.factor(sp)) %>%
  # drop stemID
  select(-ID)

data("ex_study_region")

# set max dist
max_dist <- 1

# add buffer
ex_growth_df <- ex_growth_df %>%
  add_buffer_variable(direction = "in", size = max_dist, region = ex_study_region)

ggplot() +
  geom_sf(data = ex_growth_df, aes(col = buffer), size = 2)

set.seed(76)
ex_cv_grid <- spatialBlock(
  speciesData = ex_growth_df, theRange = 5, verbose = FALSE, k = 2
)

bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = cv_fold_size, verbose = FALSE,
  # Some guess work in figuring this out:
  k = 28, xOffset = 0.5, yOffset = 0
)

bw_cv_grid_sf <- bw_cv_grid$blocks %>%
  st_as_sf()
